---
title: "Quality standard service improvement templates (QSSIT) downloads"
author: "Impact team"
date: "`r Sys.Date()`"
output: 
    html_document:
        toc: TRUE
        toc_float: TRUE
        code_folding: "hide"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(DT)
library(zoo)
library(kableExtra)
library(plotly)
library(reactable)

```

# Methods

Downloads data was exported from the prototype [health and social care dashboard](https://datastudio.google.com/u/0/reporting/f35ae256-7912-4f05-8838-79937f289faf/page/p_oqpodkxvuc), which displays Google Analytics data from the NICE website. 

Google Analytics samples a fraction of all web activity, therefore for greater accuracy, the time periods specified when extracting results were one-month rather than one-year periods. This was done by manually selecting each month in the date range widget and exporting the Downloads table in the ['All webpages:links and downloads' tab](https://datastudio.google.com/u/0/reporting/f35ae256-7912-4f05-8838-79937f289faf/page/p_ha6m8qvdtc).

Downloads were pulled for June 2019 to April 2022.

The dashboard currently does not allow for filtering by the downloaded file's URL. The exported Downloads table therefore covers all downloads from across the whole NICE website. QSSIT downloads were identified by filtering the data set for rows where the file URL includes 'QS-service-improvement-template' or 'quality-standard-service-improvement-template'. This relies on the naming system being consistent over time, which is not necessarily the case.

<button class="btn btn-primary" data-toggle="collapse" data-target="#raw_data"> Show/hide raw data </button>  
<div id="raw_data" class="collapse">  

```{r read}
data <- read_csv('./download_analytics/qssit_downloads_2019-06_2022-04.csv', col_types = "Dccd") %>% 
    mutate(qs = if_else(str_detect(page_path, "/qs\\d+/resources"), 
                        str_extract(page_path, "(?<=/)qs\\d+(?=/resources)") %>% str_to_upper(.), 
                        "general")) %>% 
    relocate(downloads,
             .after = last_col())

data %>% 
    select(!qs) %>% 
    datatable(.,
          filter = "top",
          colnames = c("Month" = "year_month",
                       "Download page" = "page_path",
                       "File URL" = "file",
                       "Downloads" = "downloads"),
          rownames = FALSE,
          extensions = 'Buttons', 
          options = list(
              dom = 'Bfrtip',
              buttons = c('csv')
  ))
```

</div>

# How much is the QSSIT being downloaded per month from across the whole NICE website?

Looking at total monthly downloads across the whole NICE website:

<button class="btn btn-primary" data-toggle="collapse" data-target="#total_downloads_data"> Show/hide total monthly downloads table </button>  
<div id="total_downloads_data" class="collapse">  

```{r}
total_downloads <- data %>% 
    group_by(year_month) %>% 
    summarise(downloads = sum(downloads))

total_downloads %>% 
    mutate(year_month = zoo::as.yearmon(year_month)) %>% 
    rename("Month" = year_month,
           "Downloads" = downloads) %>% 
    kbl() %>% 
    kable_styling(bootstrap_options = c("striped", "hover"))
```

</div>

```{r}
fig <- total_downloads %>% 
    mutate(year_month = zoo::as.yearmon(year_month)) %>% 
    ggplot(aes(x = year_month, y = downloads)) +
    geom_line() +
    labs(x = "Month",
         y = "Downloads",
         title = "Total monthly downloads of QSSIT")
    

fig %>% ggplotly()
```

# Which pages are the QSSIT being downloaded from?

The QSSIT sits on many pages, namely:

- the 'Tools and resources' tab of *every single* quality standard, e.g. [for QS206 (the latest QS)](https://www.nice.org.uk/guidance/qs206/resources),
- the '[How to use quality standards](https://www.nice.org.uk/standards-and-indicators/how-to-use-quality-standards)' page, under 'Standards and indicators' in the navigation bar,
- the '[Measuring the use of NICE guidance](https://www.nice.org.uk/about/what-we-do/into-practice/measuring-the-uptake-of-nice-guidance)' page, under 'About > Into practice' in the navigation bar,
- the very hidden '[Audit and service improvement](https://www.nice.org.uk/about/what-we-do/into-practice/audit-and-service-improvement)' page, also under 'Into practice', and more recently,
- the '[About quality standards](https://www.nice.org.uk/standards-and-indicators/quality-standards)' page, also under 'Standards and indicators'

Where do people download the QSSIT from?

```{r}
data <- data %>% 
    mutate(source_page = case_when(str_detect(page_path, "/qs\\d+/resources") ~ "Specific QSs (qs__/resources)",
                              TRUE ~ page_path) %>% 
               str_remove("\\?.*") %>% 
               str_remove("^((www.nice.org.uk/about/what-we-do/)|(www.nice.org.uk/))") %>% 
               fct_infreq())

fig_source_bar <- data %>% 
    group_by(year_month, source_page) %>% 
    summarise(downloads = sum(downloads), .groups = "drop") %>% 
    ggplot(aes(x = year_month, y = downloads, fill = source_page)) +
    geom_col(position = "stack") +
    labs(x = "Month",
         y = "Downloads",
         title = "Monthly downloads of QSSIT, by category of page downloaded from",
         fill = "Page source")

fig_source_bar %>% ggplotly(width = 850) 

```

From the bar chart above, it is clear that the contribution of different pages to overall monthly QSSIT downloads has changed over time. 

Notably, downloads from the '[How to use quality standards](https://www.nice.org.uk/standards-and-indicators/how-to-use-quality-standards)' page have dropped markedly. Since November 2021, some of the usual traffic there may have been redirected to the new '[About quality standards](https://www.nice.org.uk/standards-and-indicators/quality-standards)' page.

Looking at time trends for each page category:

```{r}

fig_source_line <- data %>% 
    group_by(year_month, source_page) %>% 
    summarise(downloads = sum(downloads), .groups = "drop") %>% 
    ggplot(aes(x = year_month, y = downloads, colour = source_page)) +
    geom_line() +
    labs(x = "Month",
         y = "Downloads",
         title = "Monthly downloads of QSSIT, by category of page downloaded from",
         colour = "Page source")

fig_source_line %>% ggplotly(width = 850) 

```

For all-time downloads by page category:

<button class="btn btn-primary" data-toggle="collapse" data-target="#all_time_category"> Show/hide all-time downloads by page category </button>  
<div id="all_time_category" class="collapse">  

<br />

Aggregating downloads by page category over the whole time period (June 2019 - April 2022), people mostly download the QSSIT from the 'Tools and resources' tab of individual quality standards.

Note, this aggregation masks the time trends shown in the line graph above.

```{r}
data %>% 
    group_by(source_page) %>% 
    summarise(downloads = sum(downloads)) %>%
    arrange(desc(downloads)) %>% 
    rename("Download page category" = source_page,
           Downloads = downloads) %>% 
    kbl() %>% 
    kable_styling(bootstrap_options = c("striped", "hover"))
```

</div>

## Looking at individual pages

How do downloads from individual quality standards' webpages compare with downloads from the general *standards and indicators* or *into practice* pages? 

The graph below disaggregates the 'Specific QSs' group and displays downloads from each individual quality standard webpage separately.

*(Interaction suggestions:*

- *Double-click on the 'Specific QSs (qs__/resources)' in the legend to isolate the specific quality standards*
- *Drag a rectangle over the data points in the graph to zoom in*
- *Hover over to see which QS the data point represents)*

```{r}
fig_qs <- data %>% 
    ggplot(aes(x = year_month, y = downloads, colour = source_page, label = qs)) +
    geom_point() +
    labs(x = "Month",
         y = "Downloads",
         title = "Monthly downloads of QSSIT, by individual pages",
         colour = "Page source")

fig_qs %>% ggplotly(width = 850)

```

Summing downloads over the whole of June 2019 to April 2022, the QSSIT is downloaded more from some quality standards than others. 

Note, these overall downloads are confounded by *when* a quality standard was released.

```{r}
data %>% 
    filter(qs != "general") %>% 
    select(-c(page_path, file, source_page)) %>%
    rename("Quality standard" = qs,
           Month = year_month,
           Downloads = downloads) %>% 
    reactable(
      .,
      filterable = TRUE,
      searchable = TRUE,
      groupBy = "Quality standard",
      showSortable = TRUE,
      columns = list(
          Downloads = colDef(aggregate = "sum",
                             sortable = TRUE)
      )
    )
```

